%-------------------------------------------------------------------------------
%PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[12pt,letterpaper]{article} % Font size (10-12pt) and
                                % paper size (a4paper, letterpaper,
                                % legalpaper, etc)

\include{Resume_sty} % Include structure.tex which contains packages
                    % and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in
                             % words with dashes where you would like
                             % hyphenation to occur, or alternatively,
                             % don't put any dashes in a word to stop
                             % hyphenation altogether
\usepackage{textcomp}
\begin{document}


%-------------------------------------------------------------------------------
%NAME AND CONTACT INFORMATION
%-------------------------------------------------------------------------------

\maintitle{Dmitri B. Ivanov, Ph.D.}{}

\noindent\textsmaller{+}1 (801) 633-2802\bull
\href{mailto:dmiivanov@gmail.com}{dmiivanov@gmail.com}\bull
\href{https://www.researchgate.net/profile/Dmitri\_Ivanov2}
{https://www.researchgate.net/profile/Dmitri\_Ivanov2}\\\bull
\href{https://github.com/ivanovdmitri}
{github.com/ivanovdmitri}

\spacedhrule{0.9em}{-0.2em}

\roottitle{Top 3 publications}
{
	\begin{itemize}
		\item {\bf ''Auger-TA Energy Spectrum Working Group Report''}
		\\{}D.~Ivanov, for the Telescope Array and Pierre Auger collaborations,
		\\{}UHECR 2018 Conf.\ Proc.\ 2019
		
		\item {\bf ''Measurement of Energy Spectrum of Ultra-High Energy Cosmic Rays''}
		\\{}V.~Verzi, D.~Ivanov and Y.~Tsunesada,
		\\{}PTEP {\bf 12} 12A103 (2017)
		
		\item {\bf ''The Cosmic Ray Energy Spectrum Observed with the Surface Detector of the Telescope Array Experiment''}
		\\{}[Telescope Array Collaboration],
		\\{}Astrophys.\ J.\  {\bf 768}, L1 (2013)
	\end{itemize}
}

\roottitle{Oral Presentations}
{
	\begin{itemize}
		\item August  29  2019: 8th International Conference on New Frontiers in Physics, Kolymbari, Crete, Greece, title: \href{https://indico.cern.ch/event/754973/contributions/3539439/}{"Telescope Array Experiment"}.
		\item July    7,  2019: The 36th International Cosmic Ray Conference, Madison, Wisconsin, title \href{http://meetings.aps.org/Meeting/APR19/Session/G08.2}{"Energy Spectrum Measured by the Telescope Array Experiment"}.
		\item April   13, 2019: 2019 April Meeting of the American Physical Society, Denver, Colorado, title \href{https://www.icrc2019.org/uploads/1/1/9/0/119067782/ivanov_icrc2019_ta_spectrum.pdf}{"Energy Spectrum Measured by the Telescope Array Experiment"}.
		\item October 8,  2018: 2018 Conference on Ultrahigh Energy Cosmic Rays, Paris, France, title: \href{https://indico.in2p3.fr/event/17063/contributions/64364/}{"Auger-TA Energy Spectrum Working Group Report"}.
		\item October 8,  2018: 2018 Conference on Ultrahigh Energy Cosmic Rays, Paris, France, title: \href{https://indico.in2p3.fr/event/17063/contributions/64389/}{"TA Spectrum"}.
		\item August  8,  2018: TeV Particle Astrophysics, Berlin, Germany, title "Telescope Array Experiment".
		\item April   15, 2018: 2019 April Meeting of the American Physical Society, Columbus, Ohio, title: \href{https://meetings.aps.org/Meeting/APR18/Event/326162}{"Anisotropy Results of the Telescope Array Experiment"}.
		\item August  4,  2017: The 35th International Cosmic Ray Conference, Busan, South Korea, 
								title \href{https://pos.sissa.it/301/498/pdf}{"Report of the Telescope Array - Pierre Auger Observatory Working Group on Energy Spectrum"}.
		\item May     9,  2017: Interplay between Particle and Astroparticle Physics, Madison, Wisconsin, title \href{https://events.icecube.wisc.edu/event/82/contributions/5218/}{"Telescope Array Experiment"}.
		\item October 11, 2016: 2016 Conference on Ultrahigh Energy Cosmic Rays, Kyoto, Japan, title: \href{https://indico.cern.ch/event/504078/contributions/2305993/}{"TA Spectrum Summary"}.
		\item April    4, 2016: 2016 April Meeting of the American Physical Society, Salt Lake City, Utah, title: \href{http://meetings.aps.org/Meeting/APR16/Session/R11.6}{"Search for EeV Protons of Galactic Origin"}.
		\item December 4, 2015: Astrophysical Multimessenger Observatory Network, State College, PA, title \href{https://sites.psu.edu/amonworkshop/wp-content/uploads/sites/34307/2015/12/Ivanov_TA_AMON.pdf}{"Telescope Array Experiment"}.
		\item August   4, 2015: The 34th International Cosmic Ray Conference, The Hague, Netherlands, title \href{https://pos.sissa.it/236/349/pdf}{"TA Spectrum Summary"}.
		\item April   14, 2015: (Invited) 2015 April American Physical Society, Baltimore, Maryland, title: \href{http://meetings.aps.org/Meeting/APR15/Session/Y9.3}{"Recent Results of the Telescope Array Experiment"}.
		\item October 13, 2014: 2014 Conference on Ultrahigh Energy Cosmic Rays, Springdale, UT, title: \href{http://uhecr2014.telescopearray.org/finished/ivanov/ivanov_uhecr2014.pdf}{"High Energy Spectrum Measured by the Telescope Array Experiment"}. 
	\end{itemize}
}

\roottitle{Publications}
{
\begin{itemize}
	
	%\cite{Ivanov:2020rqn}
	\item {\bf ''Energy Spectrum Measured by the Telescope Array Experiment''}
	\\{}D.~Ivanov for the Telescope Array collaboration
	\\PoS \textbf{ICRC2019}, 298 (2020)

	\item {\bf ''Observation of the Origin of Downward Terrestrial Gamma-Ray Flashes''}
	\\{}[Telescope Array collaboration],
    \\{} Accepted by JGR - Atmospheres as of 10/2020 
	
	\item {\bf ''Using deep learning to enhance event geometry reconstruction for the telescope array surface detector''}
	\\{}D. Ivanov, O. Kalashev, M. Kuznetsov, G. Rubtsov, T. Sako, Y. Tsunesada, and Y. Zhezher
	\\{} Accepted by Machine Learning Science and Technology as of 08/2020

	\item{}Astrophys. J. \textbf{899}, no.1, 86 (2020)	
	\item Mon.Not.Roy.Astron.Soc. 492 (2020) no.3,  3984–3993
	\item JETP 158 (2020) (8(2))
	
	\item {\bf ''Auger-TA Energy Spectrum Working Group Report''}
	\\{}D.~Ivanov, for the Telescope Array and Pierre Auger collaborations
	\\{}UHECR 2018 Conf.\ Proc.\ 2019
	
	\item Astropart.\ Phys.\  {\bf 110}, 8-14 (2019)
	
	\item {\bf ''Auger-TA Energy Spectrum Working Group Report''}
    \\{}D.~Ivanov, for the Telescope Array and Pierre Auger collaborations
    \\{}UHECR 2018 Conf.\ Proc.\ 2019
	
	\item {\bf ''Energy Spectrum Measured by the Telescope Array Experiment''}
	\\{}D.~Ivanov, for the Telescope Array collaboration
	\\{}ICRC 2019 Conf.\ Proc.\ PoS(ICRC2019)298
	
	\item Astrophys.\ J.\ Lett.  {\bf 867} L27 (2018)
	
	\item {\bf ''Evidence for Declination Dependence of Ultrahigh Energy Cosmic Ray Spectrum in the Northern Hemisphere''}
    \\{}[Telescope Array collaboration],
    \\{}[arXiv:1801.07820 [astro-ph.HE]]
	
	\item {\bf ''TA Spectrum''}
	\\{}D.~Ivanov, for the Telescope Array collaboration
	\\{}UHECR 2018 Conf.\ Proc.\ 2019
	
	\item {\bf ''The Knee and the Second Knee of the Cosmic-Ray Energy Spectrum''}
	\\{} T.~Abu-Zayyad, D.~Ivanov, C.C.H.~Jui, J.H.~Kim, J.N.~Matthews, J.D.~Smith, S.B.~Thomas, G.B.~Thomson, and Z.~Zundel
	\\{} [arXiv:1803.07052 [astro-ph.HE]]
	
	\item Astrophys.\ J.\  {\bf 865}, no. 1, 74 (2018)
	\item Astrophys.\ J.\  {\bf 862}, no. 2, 91 (2018)
	
	\item {\bf ''Report of the Telescope Array - Pierre Auger Observatory Working Group on Energy Spectrum''}
	\\{}D.~Ivanov, for Telescope Array and Pierre Auger collaborations
	\\{}ICRC Conf.\ Proc.\ PoS(ICRC2017)498. %(2017)
	
	\item {\bf ''Measurement of Energy Spectrum of Ultra-High Energy Cosmic Rays''}
	\\{}V.~Verzi, D.~Ivanov and Y.~Tsunesada,
	\\{}PTEP {\bf 12} 12A103 (2017)
		
	\item {\bf ''Search for Anisotropy in the Ultra High Energy Cosmic Ray Spectrum using the Telescope Array Surface Detector''}
	\\{}[Telescope Array collaboration],
    \\{}[arXiv:1707.04967 [astro-ph.HE]].
	
	\item Astropart.\ Phys.\  {\bf 87}, 1-17 (2017)
	\item Astropart.\ Phys.\  {\bf 86}, 21-26 (2017)
	\item P. G. Tinyakov, F.R. Urban, D. Ivanov, G. B. Thomson, A. H. Tirone, Mon.Not.Roy.Astron.Soc. 460 (2016) no.4, 3479-3487
	\item{\bf ''TA Spectrum Summary''}
	\\{}D.~Ivanov, for the Telescope Array Collaboration,
	\\{}ICRC Conf.\ Proc.\ (2015). %(2011)
	\item Phys.\ Rev.\ D {\bf 92}, no. 3, 032007 (2015)
	\item Astropart.\ Phys.\  {\bf 64}, 49 (2015)
	\item Astropart.\ Phys.\  {\bf 61}, 93 (2015)
	\item Nucl.\ Instrum.\ Meth.\ A {\bf 768}, 96 (2014).
	\item Astrophys.\ J.\  {\bf 794}, no. 2, 172 (2014)
	\item Astrophys.\ J.\  {\bf 790}, L21 (2014)
	\item Phys.\ Rev.\ D {\bf 88}, 112005 (2013)
	\item Astropart.\ Phys.\  {\bf 48}, 16 (2013)
	\item Astrophys.\ J.\  {\bf 777}, 88 (2013)
	\item Astrophys.\ J.\  {\bf 757}, 26 (2012)
	\item Astropart. Phys. \textbf{48}, 16-24 (2013)
	\item Nucl. Instrum. Meth. A \textbf{689}, 87-97 (2013)
	\item Nucl. Instrum. Meth. A \textbf{676}, 54-65 (2012)
	\item AIP Conf.\ Proc.\  {\bf 1367}, 181 (2011). %(2011)
	
	\item {}AIP Conf.\ Proc.\  {\bf 1367}, 185 (2011). %(2011)
	\item J.\ Phys.\ Conf.\ Ser.\  {\bf 293}, 012035 (2011). %(2011)
	\item B.~T.~Stokes, R.~Cady, D.~Ivanov, J.~N.~Matthews and G.~B.~Thomson. Astropart. Phys. \textbf{35}, 759-766 (2012)

	\item {\bf ''A Simple Parallelization Scheme for Extensive Air Shower Simulations''}
	\\{}B.~T.~Stokes, R.~Cady, D.~Ivanov, J.~N.~Matthews and G.~B.~Thomson.
	\\{}arXiv:1103.4643 [astro-ph.IM]

	\item AIP Conf.\ Proc.\  {\bf 1238}, 365 (2010). %(2010)
	\item Astrophys. J. Lett. \textbf{713}, no.1, L64-L68 (2010)
	\item Phys.\ Rev.\ Lett.\  {\bf 104}, 161101 (2010) 
	\item Nucl.\ Phys.\ Proc.\ Suppl.\  {\bf 190}, 26 (2009). %(2009)
	\item {}Astropart.\ Phys.\  {\bf 32}, 53 (2009)
	\item {}Astropart.\ Phys.\  {\bf 30}, 175 (2008)
	\item {}Astrophys.\ J.\  {\bf 684}, 790 (2008)
	%\href{http://www.slac.stanford.edu/spires/find/hep/www?irn=7679920}{SPIRES entry}
	
\end{itemize}

}

\end{document}
